---
title: "Occupancy dataset analysis - Giang Dao"
author: "Giang Dao"
reviewer: "Sven van Bezooijen"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    df_print: paged
self_contained: no

---
```{r}
library(readr)
library(tidyverse)
library(class)
library(caret)
```

# Data understanding

```{r}
url <- "https://raw.githubusercontent.com/HAN-M3DM-Data-Mining/assignments/master/datasets/KNN-occupancy.csv"
rawDF <- read_csv(url)

str(rawDF)
```
## Data preparation

The first column is only used for specifying date and time of the observations, and serves no purpose in the prediction model. Therefore, this column is removed from the dataset.

```{r}
cleanDF <- rawDF[-1]
head(cleanDF)
```

```{r}
cntOccu <- table(cleanDF$Occupancy)
propOccu <- round(prop.table(cntOccu)*100, digits = 1)

cntOccu
propOccu
```

The dataset labels should be converted from "character" into "factor" to be interpreted by the prediction model. I have also assigned abbreviations for these labels.
```{r}
cleanDF$Occupancy <- factor(cleanDF$Occupancy, levels = c("0","1"), labels = c("No","Yes")) %>% relevel("Yes")

head(cleanDF)
```

```{r}
summary(cleanDF[c("Temperature", "Light", "HumidityRatio")])
```
As the variables have different range from each other, we need to use the normalize function to rescale these variables.

```{r}
normalize <- function(x) { # Function takes in a vector
  return ((x - min(x)) / (max(x) - min(x))) # distance of item value - minimum vector value divided by the range of all vector values
}

testSet1 <- c(1:5)
testSet2 <- c(1:5) * 10

cat("testSet1:", testSet1, "\n")

cat("testSet2:", testSet2, "\n")

cat("Normalized testSet1:", normalize(testSet1), "\n")

cat("Normalized testSet2:", normalize(testSet2))

```

The normalize function is then applied to the dataset.

```{r}

cleanDF_n <- sapply(1:5,
                    function(x) {
  normalize(cleanDF[,x])
}) %>% as.data.frame()
head(cleanDF_n)
summary(cleanDF_n[c("Temperature", "Light", "HumidityRatio")])

```
After normalizing the data, we then move on to split the original dataset into training and testing sets.

```{r}
trainDF_feat <- cleanDF_n[1:4070,]
testDF_feat <- cleanDF_n[4071:8143,]

trainDF_labels <- cleanDF[1:4070,6]
testDF_labels <- cleanDF[4071:8143,6]
```

## Modeling and Evaluation

K-value stands for how many 'Neighbour' data points it looks for to make the conclusion in the model. A common used method is using the square root of total number of datapoints.

```{r}
x <- sqrt(nrow(cleanDF_n))

cleanDF_test_pred <- knn(train = as.matrix(trainDF_feat), test = as.matrix(testDF_feat), cl = as.matrix(trainDF_labels), k = x)
head(cleanDF_test_pred)
```

Finally, a confusionMatrix is created to show how well the model performed.

```{r}

confusionMatrix(cleanDF_test_pred, testDF_labels[[1]], positive = NULL, dnn = c("Prediction", "True"))

```
The overall performance of the model is quite good with accuracy reaching 96%.

# Reviewer's comment:

In the data prep. It is mentioned it is the column with no relevant data. But with a “-5”, the wrong column is selected from the set. With later not all of the relevant ones selected.

Furthermore in Line 74. In the code. There is tried to pass the var x from a function to a method within the code block. But this isn’t a numerical number.

While refactoring. No relevel formula was used. Which doesnt make the analysis correct

In the code block for line 80. The selection of data is done wrong. It isn’t selected how many for each set of the feat. In a good way anyway. The sets should be set as followed:

trainDF_feat <- cleanDF_n[1:4070,] testDF_feat <- cleanDF_n[4071:8143,]

As well for the Labels sets. These dont reffer to the correct column

trainDF_labels <- cleanDF[1:4070,1] testDF_labels <- cleanDF[4071:8143,1]

As a global. The librarys could be grouped at the start of the RMd file. So it can be more easlily accessed
